Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-08 main.tex
description algo search

%\newcommand{\A}{\mathcal{A}}
%\newcommand{\B}{\mathcal{B}}
\newcommand{\D}{\mathbb{D}}
\newcommand{\E}{\mathbb{E}}
%\newcommand{\P}{\mathcal{P}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\W}{\mathbb{W}}
\newcommand{\Semiring}{\mathbb{S}}
\newcommand{\zero}{\mathbb{0}}
\newcommand{\one}{\mathbb{1}}
\newcommand{\dom}{\ensuremath{\mathit{dom}}}

\def\SA{\textsf{sA}\xspace}
\def\WA{\textsf{wA}\xspace}
\def\SW{\textsf{sw}\xspace}
\def\swM{\textsf{swM}\xspace}
\def\SWT{\textsf{swT}\xspace}
\def\SWA{\textsf{swA}\xspace}
\def\SWTA{\textsf{swTA}\xspace}
\def\SWVPA{\textsf{sw-VPA}\xspace}
\def\weight{\mathsf{weight}}
\def\wei{\mathsf{w}}
\def\mei{\mathsf{m}}
\def\init{\mathsf{in}}
\def\final{\mathsf{out}}
\def\Omegai{{\Omega_\mathsf{i}}}
\def\Omegac{{\Omega_\mathsf{c}}}
\def\Omegar{{\Omega_\mathsf{r}}}
\def\Sigmai{{\Sigma_\mathsf{i}}}
\def\Sigmac{{\Sigma_\mathsf{c}}}
\def\Sigmar{{\Sigma_\mathsf{r}}}
\def\Deltai{{\Delta_\mathsf{i}}}
\def\Deltac{{\Delta_\mathsf{c}}}
\def\Deltar{{\Delta_\mathsf{r}}}
\def\Phii{{\Phi_\mathsf{i}}}
\def\Phic{{\Phi_\mathsf{c}}}
\def\Phir{{\Phi_\mathsf{r}}}
\def\Phix{{\Phi_\mathsf{x}}}
\def\Phici{{\Phi_\mathsf{ci}}}
\def\Phicc{{\Phi_\mathsf{cc}}}
\def\Phicr{{\Phi_\mathsf{cr}}}
\def\Phicx{{\Phi_\mathsf{cx}}}
\def\weii{{\wei_\mathsf{i}}}
\def\weic{{\wei_\mathsf{c}}}
\def\weir{{\wei_\mathsf{r}}}
\newcommand{\weie[1]}{\wei_{#1}^\mathsf{e}}
\def\weiei{\weie[\mathsf{i}]}
\def\weiec{\weie[\mathsf{c}]}
\def\weier{\weie[\mathsf{r}]}
\def\weiex{\weie[\mathsf{x}]}
\newcommand{\ioi}[1]{\mathsf{ioi}({#1})}
\newcommand{\rank}{\mathsf{rk}}
\newcommand{\lin}{\mathsf{lin}}

@@

\section{SW Visibly Pushdown Automata}
\label{section:SWVPA}\label{sec:SWVPA}
The model presented in this section generalizes Symbolic VPA~\cite{dAntonyAlur14SVPDA}
from Boolean semirings to arbitrary semiring weight domains.
It will compute on nested words over infinite alphabets, 
associating to every such word a weight value. 
Nested words are able to describe structures of labeled trees, 
and in the context of parsing, they will be useful to 
represent AST. % parse trees.

%\subsection{Definition}
\noindent
\label{sec:SWVPA-def}
Let $\Omega$ be a countable alphabet 
%finite (large) or infinite,
that we assume partitioned into three 
subsets~$\Omegai$, $\Omegac$, $\Omegar$,
whose elements are respectively called 
\emph{internal}, \emph{call} and \emph{return} symbols.
\philippe{Là je crois qu'il faudrait expliquer ces Omega, je commence à fatiguer et je suis un
peu largué par toutes ces définitions. J'intuite qu'il s'agit des symboles, parenthèses ouvrantes
et fermantes? Pourquoi il faut un alphabet pour les parenthèses?}
% names are  coined by application to functional program verification
% \begin{itemize}
% \item a set $\Omegai$ of \emph{internal symbols} denoted $a$,
% \item a set $\Omegac$ of \emph{call symbols} denoted $\call{a}$,
% \item a set $\Omegar$ of \emph{return symbols} denoted $\return{a}$.
% \end{itemize}
Let~$\< \Semiring, \oplus, \zero, \otimes, \one>$ be a commutative and complete semiring and let  
$\bar\Phi = \< \Phii, \Phic, \Phir, \Phici, \Phicc, \Phicr>$ 
be a label theory over $\Semiring$
%In order to simplify notations, %and following the definition of Section~\ref{section:transducer}, 
%we shall write respectively 
where $\Phii$, $\Phic$, $\Phir$ and~$\Phicx$ (with $\mathsf{x} \in \{ \mathsf{i}, \mathsf{c}, \mathsf{r}\}$) 
stand respectively 
for~$\Phi_\Omegai$, $\Phi_\Omegac$, $\Phi_\Omegar$ and~$\Phi_{\Omegac, \Omega_\mathsf{x}}$.
%
%Moreover, we extend this theory with a set $\Phii$ 
%of unary functions in $\Omegai \to \Semiring$,
%closed under $\oplus$ and $\otimes$.

\begin{definition}
A \emph{Symbolic Weighted Visibly Pushdown Automata} (\SWVPA) 
over  $\Omega = \Omegai \uplus \Omegac \uplus \Omegar$, $\Semiring$ and $\bar\Phi$ 
is a tuple $A = \< Q, P, \init, \bar\wei, \final >$,
where $Q$ is a finite set of states, 
\philippe{Est-ce que tout le monde sait ce qu'est un pushdown automata? Je suppose que c'est
lié à la pile.}
$P$ is a finite set of stack symbols, 
$\mathsf{in} : Q \to \Semiring$ 
(respectively $\mathsf{out} : Q \to \Semiring$)
are functions defining the weight for entering
(respectively leaving) a state, 
and $\bar\wei$ is a sextuplet composed of the transition functions :
$\weii : Q \times P \times Q \to \Phici$,  
$\weiei : Q \times Q \to \Phii$,  
$\weic : Q \times P \times Q \times P \to \Phicc$,  
$\weiec : Q \times P \times Q \to \Phic$,  
$\weir : Q \times P \times Q \to \Phicr$,  
$\weier : Q \times Q \to \Phir$.
%and 
%$\weiex : Q \times Q \to \Phix$ 
%with $\mathsf{x} \in \{ \mathsf{i}, \mathsf{c}, \mathsf{r}\}$.
\end{definition}
%
Similarly as in Section~\ref{section:transducer}, 
we extend the above transition functions as follows
for all $q, q' \in Q$, $p \in P$, 
$a \in \Omegai$, 
$\call{c} \in \Omegac$, 
$\return{r} \in \Omegar$, 
overloading their names: % for simplicity:
\[
\begin{array}{lll}
\weii: Q \times \Omegac \times P \times \Omegai \times Q \to \Semiring & 
\weii(q, c, p, a, q') = \eta_\mathsf{ci}(c, a) & 
\mathrm{where~} \eta_\mathsf{ci} = \weii(q, p, q'),\\
%
\weiei: Q \times \Omegai \times Q \to \Semiring & 
\weiei(q, a, q') = \phi_\mathsf{i}(a) &
\mathrm{where~} \phi_\mathsf{i} = \weiei(q, q').\\
%
\weic: Q \times \Omegac \times P \times  \Omegac \times P \times Q \to \Semiring & 
\weic(q, c, p, \call{c'}, p', q') = \eta_\mathsf{cc}(c, \call{c'}) & 
\mathrm{where~} \eta_\mathsf{cc} = \weic(q, p, p', q'),\\
%
\weiec: Q \times \Omegac \times P \times Q \to \Semiring & 
\weiec(q, {\call{c}}, p, q') = \phi_\mathsf{c}({\call{c}}) &
\mathrm{where~} \phi_\mathsf{c} = \weiec(q, p, q').\\
%
\weir: Q \times \Omegac \times P \times \Omegar \times Q \to \Semiring & 
\weir(q, {\call{c}},  p, {\return{r}}, q') = \eta_\mathsf{cr}({\call{c}},  {\return{r}}) & 
\mathrm{where~} \eta_\mathsf{cr} = \weir(q, p, q'),\\
%
\weier: Q \times \Omegar \times Q \to \Semiring & 
\weier(q, {\return{r}}, q') = \phi_\mathsf{r}({\return{r}}) &
\mathrm{where~} \phi_\mathsf{r} = \weier(q, q').\\
\end{array}      
\]

@@

\noindent
The weight associated by $A$ to $s \in \Omega^*$
is defined according to empty stack semantics: 
%
\begin{equation}
A(s)  = 
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes} 
\weight_A\bigl(\config{q}{\bot}, s, \config{q'}{\bot}\bigr) 
\mathop{\otimes} \mathsf{out}(q').
\label{eq:weightA}
\end{equation}

@@

%\subsection{Properties}
\medskip\noindent
Like VPA and symbolic VPA, 
the class of \SWVPA is closed under the binary operators of the underlying semiring.
%
\begin{proposition}\label{prop:SWVPA-product}
Let $A_1$ and $A_2$ be two \SWVPA
over the same $\Omega$, $\Semiring$ and $\bar\Phi$.
There exists two effectively constructible $\SWVPA$ 
$A_1 \oplus A_2$ and $A_1 \otimes A_2$,  
such that for all $s \in \Omega^*$, 
$(A_1 \oplus A_2)(s) = A_1(s) \oplus A_2(s)$ and 
$(A_1 \otimes A_2)(s) = A_1(s) \otimes A_2(s)$.
\end{proposition}
%
\begin{proof}
The construction is essentially the same 
as in the case of the Boolean semiring~\cite{dAntonyAlur14SVPDA}.
\end{proof}

%\subsection{Best Search} 
\label{sec:best}\label{sec:search}
\noindent
%**hypotheses**
Let us assume that the semiring~$\Semiring$ is
commutative, bounded, and complete,  
\florent{total?}
and that $\bar\Phi$ is an effective label theory.
%s.t. for all $\phi \in \Phii$, 
%$\psi \in \Phir$, 
%and $\eta \in \Phicr$, 
%$\displaystyle\bigoplus_{a \in \Omegai} \phi(a)$ 
%$\displaystyle\bigoplus_{r \in \Omegar} \phi(r)$ and 
%$\displaystyle\bigoplus_{{\call{c}} \in \Omegac} 
%\displaystyle\bigoplus_{{\return{r}} \in \Omegar} \eta({\call{c}}, {\return{r}})$
%are computable...
% 
% total ? 
% monotonic and superior writ natural ordering
%Regarding the infinite sum operator, note that
%$\bigoplus_{x \in \Phi_\Omega} \phi(x)$, 
%$\bigoplus_{y \in \Phi_\Delta} \psi(y)$, and  
%... exist and in $\Semiring$.
%
We propose a Dijkstra algorithm computing, for a $\SWVPA$ $A$
over~$\Omega$, $\Semiring$ and~$\bar\Phi$, 
the minimal weight %\wrt~$\leq_\oplus$, 
for a word in~$\Omega^*$.
%
\noindent
%More precisely, 
We distinguish two cases : when the stack is empty, and when it is not. 
\lydia{introduced 2 cases for b}
%
In the case of an empty stack, let $b_\bot : Q \times Q \to \Semiring$ be such that : %the function:
%
\begin{equation}\label{eq:bbot}
  b_\bot(q, q') = \bigoplus_{s\in \Omega^*} 
  \textstyle
  \weight_A\bigl(\config{q}{\bot}, s, \config{q'}{\bot}\bigr).
\end{equation}
%
Since $\Semiring$ is complete, the infinite sum in \eqref{eq:bbot} is well defined,
and, providing that $\Semiring$ is total, it is the minimum in $\Omega^*$,
\wrt~$\leq_\oplus$, % this ordering.
of the fonction 
$s \mapsto \weight_A(\config{q}{\sigma}, s, \config{q'}{\sigma})$.
%
The term $\config{q}{\bot}, s, \config{q'}{\bot}$ 
of this sum is the central expression in 
the definition \eqref{eq:weightA} of $A(s_0)$, for the minimum $s_0$
of the function $\weight_A$.
\lydia{so ?}

@@

%\medskip
\noindent
In order to obtain effectively a witness 
(word of $\Omega^*$ with a computation of $A$ of minimal weight), 
we require the additional property of convexity of weight functions.

\begin{proposition}\label{th:best-search}
For a \SWVPA $A$ 
over $\Omega$, 
$\Semiring$ commutative, bounded, total and complete, %semiring 
and $\bar\Phi$ effective, %and $k$-convex, % label theory,
one can construct in PTIME a word $t \in \Omega^*$ 
such that $A(t)$ is minimal \wrt the natural ordering for $\Semiring$. 
\end{proposition}

@@

the problem of searching the best derivation (AST) of a weighted CF-grammar  
that yields a given input word.

@@

obtained from the weighted CF grammar.

@@

assuming \eg that $\Omegai$ contain the symbols labelling the leaves of $\tau$ (symbols of rank $0$) 

@@

With this representation, the projection $\lin(t)|_\Omegai$ is then the 
sequence of leaves of $\tau$. %, enumerated in a \emph{dfs}-traversal. 

@@

We show in Appendix~\ref{sec:trees} how to convert a ($\SW$) tree automaton~$A$ 
%(in particular a TA computing on the AST of a given CF-grammar)
into a $\SWVPA$ computing $A(\lin(\tau))$ for every tree $\tau$. 
That also holds for the set of ASTs of a weighted CF-grammar.
%The purpose of the transducer $T$ is to measure a distance between input and output words, 
%\ie between the word $s$ and the sequence leaves of a derivation tree, in $\Omegai^*$.
%that generates (weighted) trees by replacement of a state symbol~$q_0$ (non-terminal), 
%by a tree $a(q_1,\ldots, q_k)$, where $k = \rank(a)$.
%A replacement rule $q_0 \to a(q_1,\ldots, q_k)$, 
%of weight $\wei(q_0, a, q_1 \ldots q_k) \in \Semiring$ 
%according to Definition~\ref{def:SWTA}, 
%corresponds to the production rule $q_0 := a(q_1,\ldots, q_k)$ of a weighted CF grammar,
%with set non-terminal symbols $Q$ and set of terminal symbols $\Omega_0$.
%This actually is a slight generalization of CFG since 
%each such production rule is labelled by  a symbol of $\Omega_{>0}$, 
%hence parse trees %derivation trees
%are trees of $\T(\Omega)$.
%Another (more original) generalization is that the set of terminal symbols 
%$\Omega_0$ may be infinite.
%The input language can also be expressed as a \SWTA, or, 
%as a particular case, as a weighted context-free grammar, 
%converted in turn into a \SWVPA following Lemma~\ref{lem:SWTA}.

>>>>

\newcommand{\A}{\mathcal{A}} % automata, VPA
\newcommand{\B}{\mathcal{B}} % automata (in constructions)
\newcommand{\C}{\mathcal{C}} % automata (in constructions)
\newcommand{\D}{\mathcal{D}}  % transducer = distance
\newcommand{\E}{\mathbb{E}}
%\newcommand{\P}{\mathcal{P}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\W}{\mathbb{W}}
\newcommand{\Semiring}{\mathbb{S}}
\newcommand{\zero}{\mathbb{0}}
\newcommand{\one}{\mathbb{1}}
\newcommand{\dom}{\ensuremath{\mathit{dom}}}

\def\SA{\textsf{sA}\xspace}
\def\WA{\textsf{wA}\xspace}
\def\SW{\textsf{sw}\xspace}
\def\swM{\textsf{swM}\xspace}
\def\SWT{\textsf{swT}\xspace}
\def\SWA{\textsf{swA}\xspace}
\def\SWTA{\textsf{swTA}\xspace}
\def\SWVPA{\textsf{sw-VPA}\xspace}
\def\VPA{\textsf{VPA}\xspace}
\def\SVPA{\textsf{sVPA}\xspace}
\def\weight{\mathsf{weight}}
\def\wei{\mathsf{w}}
\def\mei{\mathsf{m}}
\def\init{\mathsf{in}}
\def\final{\mathsf{out}}
\def\Omegai{{\Omega_\mathsf{i}}}
\def\Omegac{{\Omega_\mathsf{c}}}
\def\Omegar{{\Omega_\mathsf{r}}}
\def\Sigmai{{\Sigma_\mathsf{i}}}
\def\Sigmac{{\Sigma_\mathsf{c}}}
\def\Sigmar{{\Sigma_\mathsf{r}}}
\def\Deltai{{\Delta_\mathsf{i}}}
\def\Deltac{{\Delta_\mathsf{c}}}
\def\Deltar{{\Delta_\mathsf{r}}}
\def\Phii{{\Phi_\mathsf{i}}}
\def\Phic{{\Phi_\mathsf{c}}}
\def\Phir{{\Phi_\mathsf{r}}}
\def\Phix{{\Phi_\mathsf{x}}}
\def\Phici{{\Phi_\mathsf{ci}}}
\def\Phicc{{\Phi_\mathsf{cc}}}
\def\Phicr{{\Phi_\mathsf{cr}}}
\def\Phicx{{\Phi_\mathsf{cx}}}
\def\weii{{\wei_\mathsf{i}}}
\def\weic{{\wei_\mathsf{c}}}
\def\weir{{\wei_\mathsf{r}}}
\newcommand{\weie[1]}{\wei_{#1}^\mathsf{e}}
\def\weiei{\weie[\mathsf{i}]}
\def\weiec{\weie[\mathsf{c}]}
\def\weier{\weie[\mathsf{r}]}
\def\weiex{\weie[\mathsf{x}]}
\newcommand{\ioi}[1]{\mathsf{ioi}({#1})}
\newcommand{\rank}{\mathsf{rk}}
\newcommand{\lin}{\mathsf{lin}}

@@

\section{SW Visibly Pushdown Automata}
\label{section:SWVPA}\label{sec:SWVPA}
The model presented in this section generalizes symbolic \VPA
(\SVPA~\cite{dAntonyAlur14SVPDA}, 
 generalizing themselves \VPA~\cite{AlurMadhusudan09nested} to infinite alphabets)
from Boolean semirings to arbitrary semiring weight domains.
It will compute on nested words over infinite alphabets, 
associating to every such word a weight value. 
Nested words are able to describe structures of labeled trees, 
and in the context of parsing, they will be useful to 
represent AST. % parse trees.
\florent{see \S 5 and App.A}

%\subsection{Definition}
\noindent
\label{sec:SWVPA-def}
Let $\Omega$ be a countable alphabet 
%finite (large) or infinite,
that we assume partitioned into three 
subsets~$\Omegai$, $\Omegac$, $\Omegar$,
whose elements are respectively called 
\emph{internal}, \emph{call} and \emph{return} symbols~\cite{AlurMadhusudan09nested}.
\philippe{Là je crois qu'il faudrait expliquer ces Omega, je commence à fatiguer et je suis un
peu largué par toutes ces définitions. J'intuite qu'il s'agit des symboles, parenthèses ouvrantes
et fermantes? Pourquoi il faut un alphabet pour les parenthèses?}
% names are  coined by application to functional program verification
% \begin{itemize}
% \item a set $\Omegai$ of \emph{internal symbols} denoted $a$,
% \item a set $\Omegac$ of \emph{call symbols} denoted $\call{a}$,
% \item a set $\Omegar$ of \emph{return symbols} denoted $\return{a}$.
% \end{itemize}
Let~$\< \Semiring, \oplus, \zero, \otimes, \one>$ be a commutative and complete semiring and let  
$\bar\Phi = \< \Phii, \Phic, \Phir, \Phici, \Phicc, \Phicr>$ 
be a label theory over $\Semiring$
%In order to simplify notations, %and following the definition of Section~\ref{section:transducer}, 
%we shall write respectively 
where $\Phii$, $\Phic$, $\Phir$ and~$\Phicx$ (with $\mathsf{x} \in \{ \mathsf{i}, \mathsf{c}, \mathsf{r}\}$) 
stand respectively 
for~$\Phi_\Omegai$, $\Phi_\Omegac$, $\Phi_\Omegar$ and~$\Phi_{\Omegac, \Omega_\mathsf{x}}$.
%
%Moreover, we extend this theory with a set $\Phii$ 
%of unary functions in $\Omegai \to \Semiring$,
%closed under $\oplus$ and $\otimes$.

\begin{definition}
A \emph{Symbolic Weighted Visibly Pushdown Automata} (\SWVPA) 
over  $\Omega = \Omegai \uplus \Omegac \uplus \Omegar$, $\Semiring$ and $\bar\Phi$ 
is a tuple $A = \< Q, P, \init, \bar\wei, \final >$,
where $Q$ is a finite set of states, 
\philippe{Est-ce que tout le monde sait ce qu'est un pushdown automata? Je suppose que c'est
lié à la pile.}
$P$ is a finite set of stack symbols, 
$\mathsf{in} : Q \to \Semiring$ 
(respectively $\mathsf{out} : Q \to \Semiring$)
are functions defining the weight for entering
(respectively leaving) a state, 
and $\bar\wei$ is a sextuplet composed of the transition functions :
$\weii : Q \times P \times Q \to \Phici$,  
$\weiei : Q \times Q \to \Phii$,  
$\weic : Q \times P \times Q \times P \to \Phicc$,  
$\weiec : Q \times P \times Q \to \Phic$,  
$\weir : Q \times P \times Q \to \Phicr$,  
$\weier : Q \times Q \to \Phir$.
%and 
%$\weiex : Q \times Q \to \Phix$ 
%with $\mathsf{x} \in \{ \mathsf{i}, \mathsf{c}, \mathsf{r}\}$.
\end{definition}
%
Similarly as in Section~\ref{section:transducer}, 
we extend the above transition functions as follows
for all $q, q' \in Q$, $p \in P$, 
$a \in \Omegai$, 
$\call{c} \in \Omegac$, 
$\return{r} \in \Omegar$, 
overloading their names: % for simplicity:
\[
\begin{array}{lll}
\weii: Q \times [\Omegac \times P] \times \Omegai \times Q \to \Semiring & 
\weii(q, c, p, a, q') = \eta_\mathsf{ci}(c, a) & 
\mathrm{where~} \eta_\mathsf{ci} = \weii(q, p, q'),\\
%
\weiei: Q \times \Omegai \times Q \to \Semiring & 
\weiei(q, a, q') = \phi_\mathsf{i}(a) &
\mathrm{where~} \phi_\mathsf{i} = \weiei(q, q').\\
%
\weic: Q \times [\Omegac \times P] \times  [\Omegac \times P] \times Q \to \Semiring & 
\weic(q, c, p, \call{c'}, p', q') = \eta_\mathsf{cc}(c, \call{c'}) & 
\mathrm{where~} \eta_\mathsf{cc} = \weic(q, p, p', q'),\\
%
\weiec: Q \times [\Omegac \times P] \times Q \to \Semiring & 
\weiec(q, {\call{c}}, p, q') = \phi_\mathsf{c}({\call{c}}) &
\mathrm{where~} \phi_\mathsf{c} = \weiec(q, p, q').\\
%
\weir: Q \times [\Omegac \times P] \times \Omegar \times Q \to \Semiring & 
\weir(q, {\call{c}},  p, {\return{r}}, q') = \eta_\mathsf{cr}({\call{c}},  {\return{r}}) & 
\mathrm{where~} \eta_\mathsf{cr} = \weir(q, p, q'),\\
%
\weier: Q \times \Omegar \times Q \to \Semiring & 
\weier(q, {\return{r}}, q') = \phi_\mathsf{r}({\return{r}}) &
\mathrm{where~} \phi_\mathsf{r} = \weier(q, q').\\
\end{array}      
\]

@@

\noindent
The weight associated by $A$ to $s \in \Omega^*$
is defined according to empty stack semantics: 
%
\begin{equation}
A(s)  = 
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes} 
\weight_A\bigl(\config{q}{\bot}, s, \config{q'}{\bot}\bigr) 
\mathop{\otimes} \mathsf{out}(q').
\label{eq:SWVPA-value}
\end{equation}

@@

%\subsection{Properties}
\medskip\noindent
Similarly to \VPA~\cite{AlurMadhusudan09nested} 
and \SVPA~\cite{dAntonyAlur14SVPDA}, 
the class of \SWVPA is closed under the binary operators of the underlying semiring.
%
\begin{proposition}\label{prop:SWVPA-product}
Let $A_1$ and $A_2$ be two \SWVPA
over the same $\Omega$, $\Semiring$ and $\bar\Phi$.
There exists two effectively constructible $\SWVPA$ 
$A_1 \oplus A_2$ and $A_1 \otimes A_2$,  
such that for all $s \in \Omega^*$, 
$(A_1 \oplus A_2)(s) = A_1(s) \oplus A_2(s)$ and 
$(A_1 \otimes A_2)(s) = A_1(s) \otimes A_2(s)$.
\end{proposition}
%
\begin{proof}
The construction is essentially the same 
as in the case of the Boolean semiring~\cite{dAntonyAlur14SVPDA}.
\florent{complete proof}
\end{proof}

%\subsection{Best Search} 
\label{sec:best}\label{sec:search}
\noindent
We shall now present a procedure for searching, for a~$\SWVPA$ $A$, 
a word %$w \in \Omega^*$ 
of minimal weight for~$A$, 
as stated in the following proposition. %\wrt~$\leq_\oplus$, 
%
\begin{proposition}\label{th:best-search}
For a \SWVPA $A$ 
over $\Omega$, 
$\Semiring$ commutative, bounded, total and complete, %semiring 
and $\bar\Phi$ effective, %and $k$-convex, % label theory,
one can construct in PTIME a word $t \in \Omega^*$ 
such that $A(t)$ is minimal \wrt the natural ordering for $\Semiring$. 
\end{proposition} 
\florent{total?}
%
Let $A = \< Q, P, \init, \bar\wei, \final >$.
%
We propose a Dijkstra algorithm computing,
for every $q, q' \in Q$, 
the minimum, \wrt $\leq_\oplus$, of the function 
$\beta_{q, q'} : t \mapsto \weight_A(\config{q}{\bot}, t, \config{q'}{\bot})$.
Let us denote by $b_\bot(q, q')$ this minimum. 
By definition of $\leq_\oplus$ it holds that:
%
\begin{equation}\label{eq:bbot}
  b_\bot(q, q') = \bigoplus_{t\in \Omega^*} 
  \textstyle
  \weight_A\bigl(\config{q}{\bot}, t, \config{q'}{\bot}\bigr).
\end{equation}
Hence, following~\eqref{eq:SWVPA-value}, and the associativity and commutativity 
and distributivity for~$\otimes$ and~$\oplus$, the minimum of~$A(t)$ is 
\(
{\displaystyle\bigoplus_{t\in \Omega^*}}
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes} 
\beta_{q, q'}(t)
\mathop{\otimes} \mathsf{out}(q')
= 
{\displaystyle\bigoplus_{q, q' \in Q}} \textstyle
\mathsf{in}(q) \mathop{\otimes} 
b_\bot(q, q')
\mathop{\otimes} \mathsf{out}(q')
\).

\noindent
In order to compute

****

over~$\Omega$, $\Semiring$ and~$\bar\Phi$, 
the minimal weight %\wrt~$\leq_\oplus$, 
for a word in~$\Omega^*$.
%

\noindent
%More precisely, 
We distinguish two cases : when the stack is empty, and when it is not. 
\lydia{introduced 2 cases for b}
%
In the case of an empty stack, let $b_\bot : Q \times Q \to \Semiring$ be such that : %the function:
%
\begin{equation}\label{eq:bbot}
  b_\bot(q, q') = \bigoplus_{s\in \Omega^*} 
  \textstyle
  \weight_A\bigl(\config{q}{\bot}, s, \config{q'}{\bot}\bigr).
\end{equation}
%
Since $\Semiring$ is complete, the infinite sum in \eqref{eq:bbot} is well defined,
and, providing that $\Semiring$ is total, it is the minimum in $\Omega^*$,
\wrt~$\leq_\oplus$, % this ordering.
of the fonction 
$s \mapsto \weight_A(\config{q}{\sigma}, s, \config{q'}{\sigma})$.
%
The term $\config{q}{\bot}, s, \config{q'}{\bot}$ 
of this sum is the central expression in 
the definition \eqref{eq:weightA} of $A(s_0)$, for the minimum $s_0$
of the function $\weight_A$.
\lydia{so ?}

@@

\noindent
In order to obtain effectively a witness 
(word of $\Omega^*$ with a computation of $A$ of minimal weight), 
we require the additional property of convexity of weight functions.

@@

the problem of searching the best derivation (AST) of a weighted CF-grammar $G$ 
that yields a given input word $w$.

@@

obtained from $G$. %the weighted CF grammar.

@@

assuming \eg that $\Omegai$ contains the symbols labelling the leaves of $\tau$ (symbols of rank $0$), 

@@

%With this representation, the projection $\lin(t)|_\Omegai$ is the 
%sequence of leaves of $\tau$. %, enumerated in a \emph{dfs}-traversal. 

@@

We show in Appendix~\ref{sec:trees} how to construct a 
%($\SW$) tree automaton~$A$ %(in particular the TA computing on the AST of a given CF-grammar)
a $\SWVPA$ $A$ such that $A(\lin(\tau))$ is the weight the AST $\tau$ of $G$.

%That also holds for the set of ASTs of a weighted CF-grammar.
%The purpose of the transducer $T$ is to measure a distance between input and output words, 
%\ie between the word $s$ and the sequence leaves of a derivation tree, in $\Omegai^*$.
%
%that generates (weighted) trees by replacement of a state symbol~$q_0$ (non-terminal), 
%by a tree $a(q_1,\ldots, q_k)$, where $k = \rank(a)$.
%A replacement rule $q_0 \to a(q_1,\ldots, q_k)$, 
%of weight $\wei(q_0, a, q_1 \ldots q_k) \in \Semiring$ 
%according to Definition~\ref{def:SWTA}, 
%corresponds to the production rule $q_0 := a(q_1,\ldots, q_k)$ of a weighted CF grammar,
%with set non-terminal symbols $Q$ and set of terminal symbols $\Omega_0$.
%
%This actually is a slight generalization of CFG since 
%each such production rule is labelled by  a symbol of $\Omega_{>0}$, 
%hence parse trees %derivation trees
%are trees of $\T(\Omega)$.
%
%Another (more original) generalization is that the set of terminal symbols 
%$\Omega_0$ may be infinite.
%
%
%The input language can also be expressed as a \SWTA, or, 
%as a particular case, as a weighted context-free grammar, 
%converted in turn into a \SWVPA following Lemma~\ref{lem:SWTA}.
%

%In practice, 
%the functions in transition might be represented by diagram such as
%Algebraic Decision Diagrams~\cite{Bahar97ADD}
